---
title: "Work Accessibility in Singapore"
output:
  html_document:
    theme: yeti
    smart: true
    highlight: textmate
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

# Setting Up Data  
1. First, load all the packages required. 
```{r}
library(maptools)
library(RColorBrewer)
library(classInt)
library(OpenStreetMap)
library(sp)
library(rgeos)
library(tmap)
library(tmaptools)
library(sf)
library(rgdal)
library(geojsonio)
library(tidyverse)
library(leaflet)
library(downloader)
library(rgdal)
library(ggplot2)
library(reshape2)
library(plotly)
library(highcharter)
library(histogram)
library(viridis)
library(methods)
library(grid)
library(spdep)
library(sp)
library(spData)
library(spatialreg)
library(spatialEco)

```

2. Read in the planning areas boundary shapefile as a Simple Features object. 
```{r}
# Read in Singapore planning areas with age group shapefile as sf object 
SGMapSF<-st_read("planning_areas_boundary/MP14_PLNG_AREA_WEB_PL.shp")
```

3. Read in the cleaned and processed 2015 mid-census data as a CSV file. 
```{r}
SGData<-read_csv("sgdata_final.csv")
```

4. Now merge the census data to our SF object by planning area name, "PLN_AREA_N". In order to create maps which include all planning areas (including those with missing census data), the first merge function with all.x allows us to that. However, this creates problems for further analysis, so create a second dataframe which drops all planning areas for which census information is missing. 
```{r}
# join the census data to SF object 
SGDataMap<-merge(x=SGMapSF, 
             y=SGData, 
             by="PLN_AREA_N", 
             all.x = TRUE)

# create second dataframe which drops all planning areas with missing information 
SGDataMap2<-merge(SGMapSF, 
             SGData, 
             by.x="PLN_AREA_N", 
             by.y="PLN_AREA_N",
             no_dups=TRUE)


```

5. However, we also need to add in the control variable for distance to the CBD, which can be calculated using the spDistN1 function from the sp package. This requires the planning areas shapefile to be an SP object. 
```{r}
# Therefore, we need to read in the planning areas shapefile as an SP object 
library(rgdal)
SgPA <- readOGR("planning_areas_boundary/MP14_PLNG_AREA_WEB_PL.shp")
# project data to Singapore's epsg string 
proj4string(SgPA) <- CRS("+init=epsg:3414")
```
```{r}
# merge the SP object with our dataframe
library(sp)

SGDataMap3<-merge(SgPA, 
             SGData, 
             by.x="PLN_AREA_N", 
             by.y="PLN_AREA_N",
             no_dups=TRUE)
# remove all rows with NA values 
 SGDataMap3_2 <- sp.na.omit(SGDataMap3) 
   dim(SGDataMap3)
   dim(SGDataMap3_2)
```

```{r}
# Then calculate the centroids of all planning areas in Singapore 
library(spdep)
coordsPA <- coordinates(SGDataMap3_2)
# plot to check that the data is correct 
plot(coordsPA)
```
```{r}
# In order to calculate Euclidean straight line distance, the coordinates must be in WGS84 

# Give our coordinates a CRS with proj4string of Singapore's SVY21 
projectedpoints<-SpatialPoints(coordsPA, proj4string=CRS("+proj=tmerc +lat_0=1.366666666666667 +lon_0=103.8333333333333 +k=1 +x_0=28001.642 +y_0=38744.572 +ellps=WGS84 +units=m +no_defs"),bbox = NULL)

# Reproject data back to WGS84 
projectedpoints2<-spTransform(projectedpoints,"+proj=longlat +datum=WGS84")

CBDpoint<-SpatialPoints(data.frame(y = 103.8521,x=1.2931))
```

```{r}
# Calculate distance of the 28 planning areas to CBD, using the coords of City Hall MRT (1.2931, 103.8521), and store in matrix 
library(sp)
results <- spDistsN1(projectedpoints2,CBDpoint,longlat=TRUE)
#join results back to our original dataframe
SGDataMap3_2@data$dist_to_CBD<- results
```

6. Now merge the dataframe containing dist to CBD with dataframe of full list of planning areas so that later on we can plot static map including planning areas with missing values. 
```{r}
mergedmap<-merge(SGDataMap3, SGDataMap3_2, by="PLN_AREA_N", all = T)
```

# Map-making with census data 
7. The code below outputs interactive leaflet maps with two layers that can be turned on and off. The first layer shows the percentage of working persons in a planning whose travel time to work is under 45 minutes. The second map shows the population densities of the different planning areas for comparison. 

```{r}
# First reproject our data back to WGS84 for mapping 
commute_map<-spTransform(SGDataMap3_2,CRS("+proj=longlat +datum=WGS84"))
```

```{r}
# this creates pop-up labels for the work commute under 45 min layer showing percentage values 
popup <- paste0("Planning Area: ", commute_map$PLN_AREA_N, "<br>", "Percent of workers reaching work under 45 min: ", round(commute_map$`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`,2))
# this creates pop-up labels for the population density layer 
popup2 <- paste0("Planning Area: ", commute_map$PLN_AREA_N, "<br>", "Population Density (/km2): ", round(commute_map$`Population Density (/km2)`,2))

# set palette and scale for the two variables 
pal <- colorNumeric(
  palette = "YlGnBu",
  domain = commute_map$`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`)

pal2<- colorNumeric(
  palette = "YlGnBu",
  domain = commute_map$`Population Density (/km2)`)

# add tiles, polygons and legend for the two layers  
map<-leaflet() %>%
  addTiles(urlTemplate = paste0('https://api.mapbox.com/styles/v1/mapbox/light-v9/tiles/256/{z}/{x}/{y}@2x?',                               'access_token=pk.eyJ1IjoiYnlvbGxpbiIsImEiOiJjanNleDR0enAxOXZ5NDRvYXMzYWFzejA','2In0.GGB4yI6z0leM1_BwGEYfiQ'),
 attribution = '<a href="https://www.mapbox.com/about/maps/" title="Mapbox" target="_blank">Mapbox ©</a> | \
                                    Map data provided by <a href="https://www.openstreetmap.org/copyright" \
                                    title="OpenStreetMap Contributors" target="_blank">OpenStreetMap © Contributors</a>')%>%
  addPolygons(data = commute_map, 
              fillColor = ~pal(`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`), 
              color = "white", 
              fillOpacity = 0.8, 
              weight = 3, 
              smoothFactor = 0.2, 
              dashArray = "3",
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                dashArray = "",
                fillOpacity = 0.7,
                bringToFront = TRUE),
              popup = popup,
              group = "Travel Time to Work") %>%
  addLegend(pal = pal, 
            values = commute_map$`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`, 
            position = "bottomright", 
            title = "Percent of Working Persons'<br>Work Commute Under 45 Min",
            labFormat = labelFormat(suffix = "%"),
            group="Travel Time to Work") %>%
  addPolygons(data=commute_map,
              fillColor=~pal2(`Population Density (/km2)`),
              color = "white", 
              fillOpacity = 0.8, 
              weight = 3, 
              smoothFactor = 0.2, 
              dashArray = "3",
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                dashArray = "",
                fillOpacity = 0.7,
                bringToFront = TRUE),
              popup = popup2,
              group = "Population Density")%>%
addLegend(pal = pal2, 
          values = commute_map$`Population Density (/km2)`, 
          position = "bottomright", 
          title = "Population<br>Density(/km2)",group="Population Density")

# add layer control to switch on/off layers 
map1<-map %>% addLayersControl(
  overlayGroups=c("Travel Time to Work", "Population Density"),
   options = layersControlOptions(collapsed = FALSE))
map1
```
```{r}
# export interactive map as widget
library(htmlwidgets)
saveWidget(map1, file="map1.html", selfcontained=FALSE)

```

8. To further examine spatial variation in the independent variables of interest, plot static maps of income and dwelling and public transport mode share variables.
```{r}
# set tmap mode to plotting to turn off interactive viewing 
tmap_mode('plot')

# Map of the high income variable 
map2<-tm_shape(SGDataMap)+
  tm_polygons("% of Working Persons with Gross Monthly Income from Work Over S$10,000",title="Monthly Income Over S$10,000(%)",legend.hist=T,palette="YlGnBu")+
  tm_credits("a)",position=c("left","top"),size=0.8)+
  tm_scale_bar(text.size=0.7,position = c("right","bottom"))+
  tm_compass(size=2,position=c("right","bottom"))+
  tm_layout(frame=FALSE,legend.outside=TRUE,legend.outside.position=c("right","bottom"),legend.height=2,legend.text.size = 0.6,legend.title.size=1,legend.position=c("right","bottom"))

# Map for 3-room HDB dwelling variable 
map3<-tm_shape(SGDataMap)+
  tm_polygons("% of Households in 3 Room Flats - 2015",title="Households in 3 Room HDB Flats (%)",legend.hist=T,palette="YlGnBu")+
  tm_credits("b)",position=c("left","top"),size=0.8)+
  tm_scale_bar(text.size=0.7,position = c("right","bottom"))+
  tm_compass(size=2,position=c("right","bottom"))+
  tm_layout(frame=FALSE,legend.outside=TRUE,legend.outside.position=c("right","bottom"),legend.height=2,legend.text.size = 0.6,legend.title.size=1,legend.position=c("right","bottom"))

# Map of distances to HDB 
map4<-tm_shape(mergedmap)+
  tm_polygons("dist_to_CBD",title="Distance to CBD (km)",legend.hist=T,palette="YlGnBu")+
  tm_credits("c)",position=c("left","top"),size=0.8)+
  tm_scale_bar(text.size=0.7,position = c("right","bottom"))+
  tm_compass(size=2,position=c("right","bottom"))+
  tm_layout(frame=FALSE,legend.outside=TRUE,legend.outside.position=c("right","bottom"),legend.height=2,legend.text.size = 0.6,legend.title.size=1,legend.position=c("right","bottom"))

# Map of transport mode share across planning areas 
map5<-tm_shape(mergedmap)+
  tm_polygons("% of Working Persons Usual Mode of Transport to Work by Public Transport - 2015",title="Public transport mode share to work (%)",legend.hist=T,palette="YlGnBu")+
  tm_credits("d)",position=c("left","top"),size=0.8)+
  tm_scale_bar(text.size=0.7,position = c("right","bottom"))+
  tm_compass(size=2,position=c("right","bottom"))+
  tm_layout(frame=FALSE,legend.outside=TRUE,legend.outside.position=c("right","bottom"),legend.height=2,legend.text.size = 0.6,legend.title.size=1,legend.position=c("right","bottom"))
              

map2
map3
map4
map5

```

```{r}
# export maps as png files 
tmap_save(map2,filename = "map2.png")
tmap_save(map3,filename = "map3.png")
tmap_save(map4,filename = "map4.png")
tmap_save(map5,filename = "map5.png")
```

# Descriptive Statistics 
## Dependent Variable 
7. The code below generates some descriptive statistics for our dependent variable - percentage of working persons' travel time to work under 45 minutes. 
```{r}
# Descriptive Statistics 
summary(SGDataMap2)

# Create histogram of dependent variable for regression model 
histplot <- ggplot(data=SGDataMap2, aes(x=`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`,y=..density..)) + geom_histogram(colour = "black", fill = "white", binwidth=3)

# this adds lines and annotations indicating the mean, median, IQR
# also adds annotation for range 
histplot1<-histplot+geom_vline(xintercept=mean(SGDataMap2$`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`), colour="red", size=1) + geom_vline(xintercept=median(SGDataMap2$`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`), colour="blue", size=1)+geom_density(colour="red", size=1, adjust=1)+geom_vline(xintercept=65.94, colour="dark green", size=1)+geom_vline(xintercept=81.26, colour="dark green", size=1)+
annotate("text", x=60, y=0.04, label="IQR:15.32")+annotate("text", x=60, y=0.045, label="Range:37.96")+annotate("text", x=90, y=0.04, label="Mean:73.13")+annotate("text", x=90, y=0.035, label="Median:73.67")

histplot1

# export histogram 
ggsave("myplot.png", plot = histplot1)

```

## Independent Variables 
8. Next,we can also plot histograms of the selected independent variables in our final model. 

```{r}
# To plot histogram for CBD dist variable, we need to convert our sp dataframe into sf 

SGDataMapSF2<-st_as_sf(SGDataMap3_2)
```


```{r}
# Plot faceted histograms for some independent variables  
list1 <- as.data.frame(cbind(lapply(SGDataMapSF2, class)))
list1 <- cbind(list1, seq.int(nrow(list1)))
SGSub<-SGDataMapSF2[,c(1:2,15:49)]

library(sf)
library(reshape2)
# Set geometry to null to avoid errors 
# Pull out subsets for better visualisation of histogram plots 
SGSub2 <- st_set_geometry(SGSub[,c(1:2,3:5)],NULL)
SGSub3 <- st_set_geometry(SGSub[,c(1:2,11:13)],NULL)
SGSub4 <- st_set_geometry(SGSub[,c(1:2,18:20)],NULL)
SGSub5 <- st_set_geometry(SGSub[,c(1:2,37)],NULL)

# Histograms of transport mode variable
SGMelt2 <- melt(SGSub2, id.vars = 1:2)
attach(SGMelt2)
hist2 <- ggplot(SGMelt2, aes(x=value)) + geom_histogram(aes(y = ..density..),binwidth=3) + geom_density(colour="red", size=1, adjust=1.5)
hist2<-hist2 + facet_wrap(~ variable, scales="free")

# Histograms of dwelling variables 
SGMelt3 <- melt(SGSub3, id.vars = 1:2)
attach(SGMelt3)
hist3 <- ggplot(SGMelt3, aes(x=value)) + geom_histogram(aes(y = ..density..),bins=10) + geom_density(colour="red", size=1, adjust=1)
hist3<-hist3 + facet_wrap(~ variable, scales="free")

#Histograms of income variables 
SGMelt4 <- melt(SGSub4, id.vars = 1:2)
attach(SGMelt3)
hist4 <- ggplot(SGMelt4, aes(x=value)) + geom_histogram(aes(y = ..density..),bins=10) + geom_density(colour="red", size=1, adjust=1)
hist4<-hist4 + facet_wrap(~ variable, scales="free")

#Histogram of dist to CBD variable 
SGMelt5 <- melt(SGSub5, id.vars = 1:2)
attach(SGMelt3)
hist5 <- ggplot(SGMelt5, aes(x=value)) + geom_histogram(aes(y = ..density..),bins=10) + geom_density(colour="red", size=1, adjust=1)
hist5<-hist5 + facet_wrap(~ variable, scales="free")

hist2
hist3
hist4
hist5

```

# Testing for Spatial Autocorrelation in Work Accessibility Values 

9. Before calculating Moran’s I and any similar statistics, we need to first define a spatial weights matrix. We will first use Queen's contiguity, which considers polygons with a shared edge or corner for the target polygon. 
```{r}
library(spdep)
#create a neighbours list
SGPA_nb <- poly2nb(SGDataMap3_2, queen=T)
#plot them
plot(SGPA_nb, coordinates(coordsPA), col="red")
#add a map underneath
plot(SGDataMap3, add=T)
```

Now create a spatial weights object from these weights 
```{r}
SGPA.lw <- nb2listw(SGPA_nb, style="C")
head(SGPA.lw$neighbours)
```

10. Now we can calculate Moran's I and other statistics. 
```{r}
I_SGPA_Global <- moran.test(SGDataMap3_2@data$`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`, SGPA.lw)
I_SGPA_Global
```

We also calculate the Geary's C (between 0 and 2) which indicates whether similar or dissimilar values are clustering. 
```{r}
C_SGPA_Global<- geary.test(SGDataMap3_2@data$`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`, SGPA.lw)
C_SGPA_Global
```

We also calculate the Getis Ord General G which indicates if high or low values are clustering. 
```{r}
G_SGPA_Global <- globalG.test(SGDataMap3_2@data$`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`, SGPA.lw)
G_SGPA_Global
```

11. However, we also want to examine spatial autocorrelation in closer detail for each planning area. Therefore, we also calculate the local Moran's I and a Getis Ord Gi* to see where hot and cold spots are. 

```{r}
I_SgPA_Local_WorkTravel <- localmoran(SGDataMap3_2@data$`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`, SGPA.lw)
SGDataMap3_2@data$WorkTravel_LocIz <- I_SgPA_Local_WorkTravel[,4]

#Set breaks manually based on the rule that data points >2.58 or <-2.58 standard deviations away from mean are significant at the 99% level (<1% chance that autocorrelation not present); >1.96 - <2.58 or <-1.96 to >-2.58 standard deviations are significant at the 95% level (<5% change that autocorrelation not present). >1.65 = 90% etc.
breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
MoranColours<- rev(brewer.pal(8, "RdGy"))

# map the results of local Moran's I 
tmap_mode('view')
tm_shape(SGDataMap3_2) +
    tm_polygons("WorkTravel_LocIz",
        style="fixed",
        breaks=breaks1,
        palette=MoranColours,
        midpoint=NA,
        title="Local Moran's I, Travel Time Below 45 Minutes")
```

Now map the Gi* output. 
```{r}

Gi_SGPA_Local <- localG(SGDataMap3_2@data$`% of Working Persons' Travel Time to Work Up to 45 Min - 2015`, SGPA.lw)
SGDataMap3_2@data$BLocGiRz <- Gi_SGPA_Local

GIColours<- rev(brewer.pal(8, "RdBu"))

#now plot on an interactive map
tm_shape(SGDataMap3_2) +
    tm_polygons("BLocGiRz",
        style="fixed",
        breaks=breaks1,
        palette=GIColours,
        midpoint=NA,
        title="Gi*, Travel Time Under 45 Minutes")
```

# OLS Regression
18. To carry out multiple regression of factors affecting work accessibility, both the initial model and refined OLS model are run below. 

```{r}
# Initial model with possible variables 

testmodel<-lm(`% of Working Persons' Travel Time to Work Up to 45 Min - 2015` ~`% of Working Persons with Gross Monthly Income from Work Over S$10,000`+`% of Households in 3 Room Flats - 2015`+`HQA University - 2015`+`% of Working Persons Occupation as Legislators/Senior Officials - 2015`+`% Females - 2015`+`% Males - 2015`+`dist_to_CBD`,data=SGDataMap3_2)

summary(testmodel)
```
We remove all insignificant variables and end up with the following model. 
```{r}
model1 <- lm(`% of Working Persons' Travel Time to Work Up to 45 Min - 2015` ~ `% of Working Persons with Gross Monthly Income from Work Over S$10,000`+`% of Households in 3 Room Flats - 2015`+`dist_to_CBD`, data = SGDataMap3_2)

#show the summary of those outputs
summary(model1)

# save residuals 
SGDataMap3_2$model1_resids <- model1$residuals
```

19. We need to now check that the five assumptions for linear regression have been satisfied. Firstly, there must be a linear relationship between the y and x variable. Second, the residuals must be normally distributed. Third, there is no multicollinearity between the x variables. 
```{r}
library(car)
```

```{r}
# Assumption 1 - linear relationship 
q1<- qplot(x = `% of Working Persons with Gross Monthly Income from Work Over S$10,000`, y = `% of Working Persons' Travel Time to Work Up to 45 Min - 2015`,data=SGDataMap2)
q2<-qplot(x = `dist_to_CBD`, y = `% of Working Persons' Travel Time to Work Up to 45 Min - 2015`, data=SGDataMapSF2)  
q3<-qplot(x = `% of Households in 3 Room Flats - 2015`, y = `% of Working Persons' Travel Time to Work Up to 45 Min - 2015`, data=SGDataMap2)

# plot with regression line 
q1 + stat_smooth(method="lm", se=FALSE, size=1)
q2 + stat_smooth(method="lm", se=FALSE, size=1)
q3 + stat_smooth(method="lm", se=FALSE, size=1)
```

```{r}
# Assumption 2 - residuals are normally distributed
qplot(model1$residuals) + geom_histogram(bins=12) 
```

```{r}
# Assumption 3 - No multicollinearity 
vif(model1)
```
```{r}
# Assumption 3 - No multicollinearity
# this further calculates correlations for ALL the variables in the dataframe, not just the ones used in the regression 
library(corrplot) 
tempdf <- st_set_geometry(SGDataMapSF2,NULL)
cormat <- cor(tempdf[13:49], use="complete.obs", method="pearson")
str(tempdf)
corrplot(cormat, type = "lower", tl.cex = 0.5)
```

```{r}
# Assumption 4 - Homoscedascity 
# Print model diagnositcs. 
plot(model1)
```

```{r}
# Assumption 5 - Independence of Errors/No autocorrelation
#run durbin-watson test
durbinWatsonTest(model1)
```

20. Given that we are using spatially referenced data, we should be further checking for residual spatial autocorrelation using Moran's I. 

```{r}
#plot the residuals
tmap_mode("view")

tm_shape(SGDataMap3_2) +
  tm_polygons("model1_resids",
              palette = "RdYlBu") 
```

We can check for residual spatial autocorrelation more systematically with Moran's I. As we have already calculated the planning area centroids, we can jump straight into generating the spatial weights matrix. 

```{r}
# Now generate a spatial weights matrix 
library(spData)
library(spdep)

#First create a neighbours list of queen's contiguity and nearest neighbours

SGPA_nb <- poly2nb(SGDataMap3_2, queen=T)
knn_PA <- knearneigh(coordsPA, k=4)
SGPA_knn <- knn2nb(knn_PA)
```

```{r}
#plot them
plot(SGPA_nb,coordinates(coordsPA),col='red')
```
```{r}
plot(SGPA_knn, coordinates(coordsPA), col="blue")
```
```{r}
#create a spatial weights matrix object from these weights
SGPA.queens_weight <- nb2listw(SGPA_nb, style="C")
SGPA.knn_4_weight <- nb2listw(SGPA_knn, style="C")
```

Now, run the Moran's I test for residual spatial autocorrelation using both weights. 
```{r}
#now run a moran's I test on the residuals
#first using queens neighbours
moran.test(SGDataMap3_2@data$model1_resids, SGPA.queens_weight)
#with knn = 4
moran.test(SGDataMap3_2@data$model1_resids, SGPA.knn_4_weight)
```

The results show us that there is some weak spatial autocorrelation affecting our residuals, so we should try to correct for this using a spatial error model. 

# Spatial Error Regression 

21. Now we run the spatial error model. 
```{r}
sem_model1 <- errorsarlm(`% of Working Persons' Travel Time to Work Up to 45 Min - 2015` ~ `% of Working Persons with Gross Monthly Income from Work Over S$10,000`+`% of Households in 3 Room Flats - 2015`+`dist_to_CBD`, data = SGDataMap3_2, nb2listw(SGPA_nb, style="C"), method = "eigen")

# print the results of the model 
summary(sem_model1)
```
22. We also check the residuals for autocorrelation again. 
```{r}
#write out the residuals
SGDataMap3_2@data$sem_model1_resids <- sem_model1$residuals

#now test for spatial autocorrelation
moran.test(SGDataMap3_2@data$sem_model1_resids, SGPA.queens_weight)
```

23. While we can run the spatially-lagged regression model using the queen's contiguity and k-nearest neighbours, the results of residual autocorrelation were had higher p-values than the spatial error model, which explains why this method was not chosen. 
```{r}
library(spatialreg)
#run a spatially-lagged regression model with a queen's case weights matrix

slag_dv_model_queen <- lagsarlm(`% of Working Persons' Travel Time to Work Up to 45 Min - 2015` ~ `% of Working Persons with Gross Monthly Income from Work Over S$10,000`+`% of Households in 3 Room Flats - 2015`+`dist_to_CBD`, data = SGDataMap3_2, nb2listw(SGPA_nb, style="C"), method = "eigen")

#what do the outputs show?
summary(slag_dv_model_queen)
```

```{r}
#run a spatially-lagged regression model
slag_dv_model_knn4 <- lagsarlm(`% of Working Persons' Travel Time to Work Up to 45 Min - 2015` ~ `% of Working Persons with Gross Monthly Income from Work Over S$10,000`+`% of Households in 3 Room Flats - 2015`+`dist_to_CBD`, data = SGDataMap3_2, nb2listw(SGPA_knn, style="C"), method = "eigen")

#what do the outputs show?
summary(slag_dv_model_knn4)
```

Check for spatial autocorrelation. 
```{r}
#write out the residuals
SGDataMap3_2@data$slag_dv_model_knn_resids <- slag_dv_model_knn4$residuals

#now test for spatial autocorrelation
moran.test(SGDataMap3_2@data$slag_dv_model_knn_resids, SGPA.knn_4_weight)
```


